---
title: "Cronbachs alpha estimation"
format: pdf
editor: source
bibliography: references.bib
---

# Cronbach's alpha estimation with R

## Explanations of the Sections:

-   **Bonett-Formula**: Provides a mathematical way to estimate the required sample size based on desired Cronbach's Alpha, test power, confidence level, and the number of items in the test.
-   **presize package**: provides a quick way in R to calculate the required sample size of cronbachs alpha based on a different approach.
-   **R-code**: Shows how to implement the sample size calculation using the @bonett2002alpha method, as well as an alternative using the `presize` package.

## Via the Bonett-Formula

The required sample size $N$ for Cronbach's Alpha can be calculated using the **Bonett-Formula** [@bonett2002alpha]

$$
N = \frac{(Z_{\alpha/2} + Z_{\beta})^2 \cdot (1 - \alpha) \cdot k}{\alpha}
$$

### Explanations:

-   $N$ : Required sample size
-   $\alpha$: Desired Cronbach's Alpha (e.g., 0.7 or 0.8)
-   $Z_{\alpha/2}$: The critical Z-value for the confidence level (e.g., for a 95% confidence interval, the value is 1.96)
-   $Z_{\beta}$: The critical Z-value for the test power (e.g., for 80% power, the value is 0.84)
-   $k$: Number of items in the test (e.g., 10 items)

The formula calculates the minimum sample size required to achieve a desired Cronbach's Alpha with a given test power and confidence level.

### Code example

```{r}
# Input parameters
alpha1 <- 0.8     # Expected Cronbach's Alpha
alpha0 <- 0.70    # Minimum value (null hypothesis)
k <- 23           # Number of items
alpha <- 0.05     # Significance level
power <- 0.80     # Desired power

# Z-values
z_alpha <- qnorm(1 - alpha / 2)
z_beta <- qnorm(power)

# Calculation of required sample size according to Bonett (2002)
log_term <- log((1 - alpha0) / (1 - alpha1))
numerator <- (z_alpha + z_beta)^2
denominator <- log_term^2
multiplier <- (2 * (k - 1) / k)^2

n <- ceiling(numerator / denominator * multiplier)

cat("Required sample size:", n, "\n")


```

## via the `presize` - package [@presize] 

### code example

```{r}
#install.packages("presize") 

library(presize)
prec_cronb(k = 23, calpha = 0.8, n = NULL, conf.level = 0.95, conf.width = 0.1)


```

### Explanations:

-   $N$: Required sample size
-   $calpha$: expected Cronbach's Alpha (e.g., 0.7 or 0.8)
-   $conf.level$ : confidence level
-   $conf.width$: precision (the full width of the confidence interval). is 0.84)
-   $k$: Number of items in the test (e.g., 10 items)

# References
